Reading Notes

### 2020-03-20 paper.tex
merge

\cite{Vehoff2010a}
rubrene record charge carrier $15 \frac{cm^{2}}{V s}$ single crystal by vapor deposition. typical for thin-film is $1 \frac{cm^{2}}{V s}$
good discussion of some of the assumption of marcus theory. 
Drude model (electrons bounce off stationary nuclei like a pinball machine) works for perfect crystals at low temp.
At RT it doesn't work. Marcus theory assumes nuclear dynamics much slower (Borne-Oppenheimer) and electronic coupling is weak (what does this mean exactly?). Static disorder is based on the electronic DOS and the hopping rate between localized states. (As opposed to what?)
They start with single crystal structures from xray data. They calculate reorganization energies with b3lyp 6-311G(d,p) and transfer integrals with ZINDO. (check their SI)
How are they able to calculate direction-resolved transfer integrals?? very cool. What exactly do the transfer integral graphs mean? (Figure 2) Had a helpful chat with Chris about this and it helped me to think through the figures. The y-axis on the transfer integral is counts and the x-axis is energies--it makes sense that movement of an electron in different directions would require different energies and/or be more likely. Still not sure how to calculate it though.

@@

\bibliography{library}
\bibliographystyle{ieeetr}
\end{document}

>>>>

https://pubs.acs.org/doi/10.1021/ja104380c - 
rubrene record charge carrier $15 \frac{cm^{2}}{(V s)}$ single crystal by vapor deposition. typical for thin-film is $1 {cm^{2}}{(V s)}$

good discussion of some of the assumption of marcus theory. 
Drude model (electrons bounce off stationary nuclei like a pinball machine) works for perfect crystals at low temp.
At RT it doesn't work. Marcus theory assumes nuclear dynamics much slower (Borne-Oppenheimer) and electronic coupling is weak (what does this mean exactly?). Static disorder is based on the electronic DOS and the hopping rate between localized states. (As opposed to what?)
They start with single crystal structures from xray data. They calculate reorganization energies with b3lyp 6-311G(d,p) and transfer integrals with ZINDO. (check their SI)
How are they able to calculate direction-resolved transfer integrals?? very cool. What exactly do the transfer integral graphs mean? (Figure 2) Had a helpful chat with Chris about this and it helped me to think through the figures. The y-axis on the transfer integral is counts and the x-axis is energies--it makes sense that movement of an electron in different directions would require different energies and/or be more likely. Still not sure how to calculate it though.

\cite{Vehoff2010a}
rubrene record charge carrier $15 \frac{cm^{2}}{V s}$ single crystal by vapor deposition. typical for thin-film is $1 \frac{cm^{2}}{V s}$

@@

rereading the perspective paper \cite{Jankowski2019} looking for things to read next:
Braun 2018 foundations in molecular simulation
https://doi.org/10.33011/ livecoms.1.1.5957
74-89 are relevant to coarse-graining
92-95 start here for opvs

Matt Thompson got a job at OpenFF, one of the tools they list as desirable for applicants is knowledge of psi4:
https://pubs.acs.org/doi/abs/10.1021/acs.jctc.8b00286

read official papers for mosdef. check github.
\bibliography{library}
\bibliographystyle{ieeetr}
\end{document}
